Mixed effect tweedie model in TMB

### 2019-04-12 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
add loglik_cv for model comparision

#set.seed(39201114) # original seed, predictions max out at .88 cor with true temp
set.seed(392011149)
d_trawl$log_temperature_c <- log(d_trawl$temperature_c)
d_trawl$depth2 <- (d_trawl$depth_scaled)^2
d_trawl$depth3 <- (d_trawl$depth_scaled)^3
```

@@

@@

#FIXME: this is crashing R

```{r}
m_temp2_rw_poly <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled,2),
  include_spatial = FALSE, ar1_fields = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)
```

```{r}
predictions_nd <- predict(m_temp2_rw_poly, newdata = qcs_grid)
#saveRDS(predictions3_rw_nd$data, file = "qcs-temp.rds")
```

>>>>

#set.seed(39201114) # original seed, predictions max out at .88 cor with true temp
set.seed(392011149)
d_trawl$log_temperature_c <- log(d_trawl$temperature_c)
d_trawl$depth2 <- (d_trawl$depth_scaled)^2
d_trawl$depth3 <- (d_trawl$depth_scaled)^3
d_trawl$depth_scaled3 <- (d_trawl$depth_scaled)^3
```

@@

10-fold cross-validation of candidate models
```{r}
temp1 <- loglik_cv(d_trawl, n_knots = 100, 
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp1$nll)

temp2 <- loglik_cv(d_trawl, n_knots = 100, 
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp2$nll)

temp3 <- loglik_cv(d_trawl, n_knots = 100, 
                   formula = temperature_c ~ 0 + as.factor(year) + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3$nll)

# allow slope with depth to vary through between years with a random walk
temp1_rw <- loglik_cv(d_trawl, n_knots = 100,
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp1_rw$nll)

temp2_rw <- loglik_cv(d_trawl, n_knots = 100, 
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp2_rw$nll)

temp3_rw <- loglik_cv(d_trawl, n_knots = 100, 
                   formula = temperature_c ~ 0 + as.factor(year),
                   time_varying = ~ 0 + depth_scaled + depth_scaled2 + depth_scaled3,
                   time = "year", family = gaussian(link = "identity"), 
                   ar1_fields = FALSE, include_spatial = FALSE)
sum(temp3_rw$nll)
```

@@

# there is probably a problem with doing this... but need to figure out how to add poly args to predict function
```{r eval=FALSE}
m_temp2_rw_poly <- sdmTMB(d_fit,
  temperature_c ~ 0 + as.factor(year),
  time_varying =  ~ 0 + poly(depth_scaled,2),
  include_spatial = FALSE, ar1_fields = FALSE,
  time = "year", spde = spde, family = gaussian(link = "identity"),
  silent = TRUE)
```

```{r}
qcs_grid$depth2 <- (qcs_grid$depth_scaled)^2
qcs_grid$depth3 <- (qcs_grid$depth_scaled)^3
```

```{r}
predictions_nd <- predict(m_temp2_rw_nosp, newdata = qcs_grid)
#saveRDS(predictions3_rw_nd$data, file = "qcs-temp.rds")
```
